R Notebook

### 2019-08-12 analysis/final_analysis.Rmd
fix error created by new read_csv behavior

```{r}
library(jsonlite)
library(tidyverse)
library(ggthemes)
library(lme4)
library(lmerTest)
library(tidyboot)
library(coda)
library(irr)

@@

## Have to correct for post-hoc attemptNum and instructionNum bugs (got reset for next trial prematurely)
## Also, remove trials where multi-drop bug happened (i.e. where clicking multiple times triggered multiple instruction resetting)
exp2_drops <- read_csv('../data/final/experiment2/drop/dropsFromMongo.csv') %>%
  mutate(critical = ifelse(critical == 'True', 1, 0),
         correct = ifelse(correct == 'correct', 1, 0),
         instructionNum = ifelse(correct == 0, instructionNum + 1, instructionNum)) %>%
  group_by(gameid, targetObject) %>%
  filter(length(unique(instructionNum)) < 2) %>%
  group_by(gameid, instructionNum, trialNum) %>%
  mutate(attemptNum = ifelse(attemptNum == 0, max(attemptNum), attemptNum - 1)) %>%
  rename(dropTime = serverTime) %>%
  select(-X1, -eventType)
```

@@

```{r}
fillerErrors <- exp2_drops %>%
  #filter(critical != 1) %>%   # only look at mistakes on noncritical (filler) items
  filter(attemptNum == 0) %>%   # don't want to double-count people for messing the same thing up multiple times
  group_by(gameid, correct, critical, condition) %>%
  tally() %>%
  ungroup() %>%
  mutate(correct = ifelse(correct == 1, 'no_mistake', 'mistake')) %>%
  spread(correct, n, fill = 0) %>%
  mutate(numErrors = mistake, errorRate = mistake/ (no_mistake + mistake) )

nonCriticalMistakes = (fillerErrors %>%
  filter(critical == 0) %>%
  filter(numErrors >= 2))$gameid
```

@@

```{r}
exp2_subjInfo <- read_csv('../data/final/experiment2/turk/subjInfo.csv')
incompleteIDs <- unique((exp2_messages %>% 
                           group_by(gameid, trialNum, instructionNum) %>% 
                           summarize(id = row_number()) %>% 
                           group_by(gameid) %>% 
                           tally() %>% 
                           filter(n != 32))$gameid)

@@

buggyTrials <- read_csv('../data/final/experiment2/drop/dropsFromMongo.csv') %>%
  mutate(critical = ifelse(critical == 'True', 1, 0),
       correct = ifelse(correct == 'correct', 1, 0),
       instructionNum = ifelse(correct == 0, instructionNum + 1, instructionNum)) %>%
  group_by(gameid, targetObject) %>%
  mutate(numInstructions = length(unique(instructionNum))) %>%
  filter(numInstructions > 1)

>>>>

```{r}
library(jsonlite)
library(tidyverse)
library(ggthemes)
library(lme4)
library(lmerTest)
library(tidyboot)
library(coda)
#library(irr)

@@

## Have to correct for post-hoc attemptNum and instructionNum bugs (got reset for next trial prematurely)
## Also, remove trials where multi-drop bug happened (i.e. where clicking multiple times triggered multiple instruction resetting)
exp2_drops <- read_csv('../data/final/experiment2/drop/dropsFromMongo.csv') %>%
  mutate(correct = correct == 'correct',
         instructionNum = ifelse(correct == FALSE, instructionNum + 1, instructionNum)) %>%
  group_by(gameid, targetObject) %>%
  filter(length(unique(instructionNum)) == 1) %>% 
  group_by(gameid, instructionNum, trialNum) %>%
  mutate(attemptNum = ifelse(attemptNum == 0, max(attemptNum), attemptNum - 1)) %>%
  rename(dropTime = serverTime) %>%
  select(-X1, -eventType)
```

@@

```{r}
fillerErrors <- exp2_drops %>%
  filter(critical == FALSE) %>%   # only look at mistakes on noncritical (filler) items
  filter(attemptNum == 0) %>%   # don't want to double-count people for messing the same thing up multiple times
  group_by(gameid, correct, critical, condition) %>%
  tally() %>%
  ungroup() %>%
  mutate(correct = ifelse(correct, 'no_mistake', 'mistake')) %>%
  spread(correct, n, fill = 0) %>%
  mutate(numErrors = mistake, errorRate = mistake/ (no_mistake + mistake) )

nonCriticalMistakes = (fillerErrors %>%
  filter(numErrors >= 2))$gameid
```

@@

```{r}
exp2_subjInfo <- read_csv('../data/final/experiment2/turk/subjInfo.csv')
incompleteIDs <- unique((exp2_messages %>% 
                           group_by(gameid, trialNum, instructionNum) %>% 
                           summarize(nn = n()) %>% 
                           group_by(gameid) %>% 
                           tally() %>% 
                           filter(n != 32))$gameid)

@@

buggyTrials <- read_csv('../data/final/experiment2/drop/dropsFromMongo.csv') %>%
  mutate(correct = correct == 'correct',
       instructionNum = ifelse(correct == FALSE, instructionNum + 1, instructionNum)) %>%
  group_by(gameid, targetObject) %>%
  mutate(numInstructions = length(unique(instructionNum))) %>%
  filter(numInstructions > 1)
